Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

\author{\IEEEauthorblockN{1\textsuperscript{st} Beilong Tang}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bt132@duke.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Bang Zeng}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bangzeng@whu.edu.cn}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
Kunshan, China \\
zhan.jin@whu.edu.cn}
\and
\IEEEauthorblockN{4\textsuperscript{th} Ming Li}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
ming.li369@dukekunshan.edu.cn}
}

@@

\subsubsection{Training}
We use the publicly available Kmeans tokenizer and scalable 
HiFi-GAN decoder in \cite{speechbrain}. The Kmeans tokenizer
is trained on \texttt{train\_clean\_100}, \texttt{train\_clean\_360}, and \texttt{train\_other\_500} of
LibriSpeech \cite{librispeech}, and the scalable HiFi-GAN is trained on \texttt{train\_clean\_100} of 
LibriTTS \cite{libritts}. The modeling stage is trained on 
\texttt{train\_clean\_100} and \texttt{train\_clean\_360} of LibriSpeech. All training data are 
generated on the fly with relative SNR between 0 dB to 5 dB. The mixture audio is segmented to 3 
seconds and the reference speech is segmented to 4 seconds. 
We use embedding dimension \(d=1024\) and

>>>>

\author{\IEEEauthorblockN{1\textsuperscript{st} Beilong Tang}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bt132@duke.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Bang Zeng}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bangzeng@whu.edu.cn}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
% \IEEEauthorblockA{\textit{Duke Kunshan University} \\
% Kunshan, China \\
% zhan.jin@whu.edu.cn}
\and
\IEEEauthorblockN{3\textsuperscript{re} Ming Li}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
ming.li369@dukekunshan.edu.cn}
}

@@

\subsubsection{Training}
We use the publicly available Kmeans tokenizer and scalable 
HiFi-GAN decoder in \cite{speechbrain}. The Kmeans tokenizer
is trained on \texttt{train\_clean\_100}, \texttt{train\_clean\_360}, and \texttt{train\_other\_500} of
LibriSpeech \cite{librispeech}, and the scalable HiFi-GAN is trained on \texttt{train\_clean\_100} of 
LibriTTS \cite{libritts}. The modeling stage is trained on 
\texttt{train\_clean\_100} and \texttt{train\_clean\_360} of LibriSpeech. All training data are 
generated on the fly with relative SNR between 0 dB to 5 dB. The mixture audio is segmented to 3 
seconds and the reference speech is segmented to 4 seconds. 
We use embedding dimension 1024, sinusoidal positional embedding, and 4 transformer 
encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. 
We use separate embedding tables for reference and mixed speech due to our observations that not 
sharing embeddings does slightly better than sharing embeddings.
